User-level Grid Monitoring with Inca 2

### 2007-02-28 pubs/papers/hpdc-gmw-2007/paper.tex
changes to features
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6603 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\item Runs from a standard user
account in order to reflect regular user experiences.  It is important not to execute from a system administrator's account,
because it may have special privileges and use custom shell initialization files.

\item Executes with a standard user GSI
credential, which is mapped to the standard user account, when tests or performance measurements require authentication to Grid services.

\item Emulates a regular user using tests and performance
measurements that are written and configured using information directly from user documentation
(e.g., hostnames, ports, pathnames, etc.). 
This may not always be possible
when documentation and testing are done in parallel in a pre-production
environment, but they should be closely coordinated activities.

\item Centrally manages the configuration of user-level tests or performance measurements in order to ensure consistent testing of the resources, rather than
by system administrators who may not use the same information that is
available to users.

\item Is easy to update
and maintain as user-level tests and performance measurements often need
to be updated when the Grid infrastructure is upgraded.
It is also difficult to write and deploy a test correctly the first time
because of portability issues and incomplete user documentation.  Multiple
iterations are usually required to determine whether a detected failure stems
from a faulty test, user documentation, or Grid resource.

\item Provides a representative indication of Grid status by testing
documented user commands and individual Grid software components.

\item Automates the execution of user-level tests or performance measurements
periodically since Grids are dynamic.

\item Executes locally on all Grid
resources when appropriate so that all Grid access points available to users
are verified.  Similarly, it is important to execute some tests all-to-all
in order to detect site-to-site configuration errors such as authentication
problems.

>>>>

\item Runs from a standard user
account in order to reflect regular user experiences.  It is important not to execute from a system administrator's account,
which may have special privileges and use custom shell initialization files.

\item Executes with a standard user GSI credential mapped to a standard user
account when tests or performance measurements require authentication to Grid
services.

\item Creates and configures tests and performance measurements based on user
documentation rather than on system administrator knowledge (of hostnames,
ports, pathnames, etc.).  This may not always be possible when documentation
and tests are developed simultaneously during pre-production, but they should
be closely coordinated activities.

\item Centrally manages the configuration of user-level tests or performance
measurements in order to ensure consistent testing across resources.

\item Easily updates and maintains user-level tests and performance
measurements.  This is important because tests and measurements are often
updated when Grid infrastructure is upgraded.  Also, it is difficult to write
and deploy a test correctly the first time due to portability issues and
incomplete user documentation.  Multiple iterations are usually required to
determine whether a detected failure stems from a faulty test, user
documentation, or Grid resource.

\item Represents overall Grid status by testing a variety of 
documented user commands and individual Grid software components.

\item Automates the periodic execution of user-level tests or performance
measurements to capture dynamic Grid status.

\item Executes locally on Grid resources to verify user accessible Grid access
points.  Executes from each resource to every other resource (all-to-all) to
detect site-to-site configuration errors such as authentication problems.
